Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
sp

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}

@@

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilizes the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
In the second approach,...}

@@

\addtodo{We have to summarize our main contributions here}

@@

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications; algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesizes invariants to
generate the desired programs.

Program synthesisers are an ideal fit for synthesis of %parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilizing continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesize.
\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesizing continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system}. The solution is based on synthesizing control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of software-implemented 
digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
technique, their approach is restricted to synthesising controllers for hybrid 
closed-loop systems that are stable and only consider transfer function models.  
In contrast, in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is that we integrate abstraction
refinement inside the CEGIS loop.

@@

The classical approach to control synthesis has often disregarded
quantization as a minimal effect, thus proving unsound in the case of digital control systems.
Modern techniques focus on different elements of the discretization effect, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
the goal to either verify (e.g.~\cite{daes20161}) or optimize
(e.g.~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilization as an invariant set that always converges toward the controllable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and binds their trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a `buffer' region for the safety specification.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined
In this section we outline the general architecture of the program synthesiser used in both approaches%\todo{which approaches?}. 
We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesiser}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ \todo{now variables are vectorised, however previously the model variables aren't. please align notation. I do not like to use vectors unless essential, let's say it's a waste of ink in printouts. }
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

At this point, we recap the the synthesis problem that we solve in this work:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be set to zero.  
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_c,F_c\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesise a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

Proof. 
Consider the set of initial states, $X_0$, assumed to be convex since it's a box. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. 
So then if $x_0=x$, then $x_k = (A_d - B_d K)^k x = 
(A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i = 
\sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i  = 
\sum_{i=1}^{2^n} \alpha_i x_k^i$, 
where I have denoted with $x_k^i$ the trajectories obtained from the single vertices $v_i$.QED

@@

For a stabilized closed-loop, which is necessary for our safety property, we need
these roots to remain within the unit circle, which we verify using Jury's criteria.
Notice that in our polynomials $c_0=1$ and we only use reals.
\todo{where is $\phi_{input}$ computed?}
Once we have established convergence, we may examine the 
specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
% Whilst there are other properties, we may include in the verification, 
% we will solely focus on these for simplicity of the explanation.
% We assume that we do not want saturation in our system, 
% hence the control loop has only one mode.

@@

\begin{enumerate}
\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
\end{enumerate} 
\item If the candidate solution is not valid we refine the abstraction used by the synthesiser
\begin{enumerate}
\item Find the constraints that invalidate the property. These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\phi(\Lambda)$. This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics. 
\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \phi_{\Lambda}$.
\item Pass the refined abstraction with the new contraints to the synthesiser, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesiser is monotonically decreasing. The first one improves speed of the tool whereas the second ensures convergence.

@@

Table~\ref{table:State-space benchmarks} summarizes all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
metal ball hanged in air via a magnetic field . 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

\textit{Automotive Cruise System} plant describes a physical model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the physical model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
with magnetic fields (typically employed in analog gauges and indicators).
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.
\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
for the yaw angle dynamics of a US warship USCG Cutter Tampa.

@@

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalize to other benchmarks.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}

@@

We describe and evaluate two approaches for synthesizing digital controllers 
for state-space physical plants. Both approaches consider a counterexample 
guided inductive synthesis (CEGIS) loop. In the first approach, 
we devise a digital controller that stabilises the system; then, we verify its 
potential safety by unfolding the dynamics of the system and checking for 
a completeness threshold. \textcolor{red}{Dario: Can you please briefly explain your approach?
In the second approach,...}

@@

\addtodo{We have to summarise our main contributions here}

@@

Program synthesis is the problem of computing correct-by-design programs
from high-level specifications; algorithms for this problem have made
substantial progress in recent years.  One such
approach~\cite{itzhaky2010simple} inductively synthesises invariants to
generate the desired programs.

Program synthesizers are an ideal fit for synthesis of %parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesise.
\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system}. The solution is based on synthesising control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilising controllers for continuous plants
by exploiting advantage in bit-accurate verification of software-implemented 
digital control~\cite{Bessa16}.  While they also make use of a CEGIS-based 
technique, their approach is restricted to synthesising controllers for hybrid 
closed-loop systems that are stable and only consider transfer function models.  
In contrast, in the current paper, we consider a state-space
representation of the physical system, which allows us to synthesise controllers that
make the closed-loop system \emph{safe} as well as stable.  Moreover, 
a key aspect of the second approach we evaluate
is that we integrate abstraction
refinement inside the CEGIS loop.

@@

The classical approach to control synthesis has often disregarded
quantization as a minimal effect, thus proving unsound in the case of digital control systems.
Modern techniques focus on different elements of the discretization effect, including delayed
response~\cite{Duggirala2015}, and Finite Word Length (FWL) semantics with
the goal to either verify (e.g.~\cite{daes20161}) or optimise
(e.g.~\cite{oudjida2014design}) given implementations.

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilisation as an invariant set that always converges toward the controllable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and binds their trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a `buffer' region for the safety specification.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{CEGIS of Safe Controllers for LTI Systems with Solution Generalisation} 
\label{sec:CEGARIS} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%Abstractly-Refined
In this section we outline the general architecture of the program synthesizer used in both approaches%\todo{which approaches?}. 
We then give the details of the two methods of solution generalisation that we compare; the first checking safety by unwinding the transition relation to a completeness threshold; and the second employing abstract acceleration.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
$\exists \vec{P} .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ where
$\vec{P}$ ranges over functions, $\vec{x}$ \todo{now variables are vectorised, however previously the model variables aren't. please align notation. I do not like to use vectors unless essential, let's say it's a waste of ink in printouts. }
 ranges over ground terms and
$\sigma$ is a quantifier-free formula.  We interpret the ground terms over
some finite domain $\mathcal{D}$.

@@

At this point, we recap the the synthesis problem that we solve in this work:
find a digital controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop system safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range
and the reference signal to be set to zero.  
When mapping back to the notation used for describing the general architecture 
of the program synthesizer, the controller $K$ denotes $P$ and 
$(x_0, u_k)$ represents $x$. 
While the controller's precision $\langle I_c,F_c\rangle$ is given, 
we can vary the plant's precision $\langle I_p,F_p\rangle$ such that 
$\mathbb{R}\langle I_p,F_p \rangle \supseteq \mathbb{R}\langle I_c,F_c \rangle$.

@@

1. The inductive synthesis phase (i.e. {\sc synthesise}) uses BMC to
compute a candidate solution $K$
that satisfies both the stability criteria detailed in 
Sec.~\ref{ssec:stability} and the safety specification in Sec.~\ref{ssec:safety}.
%% The stability criteria are satisfied if the characteristic polynomial of $A_d - B_d * K_d$ meets Jury's criteria. This is 
%% independent of the initial states. 
Regarding the latter, we synthesise a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesise} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

@@

Proof. 
Consider the set of initial states, $X_0$, assumed to be convex since it's a box. 
Name $v_i$ its vertexes, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. 
So then if $x_0=x$, then $x_k = (A_d - B_d K)^k x = 
(A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i = 
\sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i  = 
\sum_{i=1}^{2^n} \alpha_i x_k^i$, 
where I have denoted with $x_k^i$ the trajectories obtained from the single vertexes $v_i$.QED

@@

For a stabilised closed-loop, which is necessary for our safety property, we need
these roots to remain within the unit circle, which we verify using Jury's criteria.
Notice that in our polynomials $c_0=1$ and we only use reals.
\todo{where is $\phi_{input}$ computed?}
Once we have established convergence, we may examine the 
specification of the state and input spaces ($\phi_{safety} \wedge \phi_{input}$).
% Whilst there are other properties, we may include in the verification, 
% we will solely focus on these for simplicity of the explanation.
% We assume that we do not want saturation in our system, 
% hence the control loop has only one mode.

@@

\begin{enumerate}
\item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{tp},\mathcal{B}_{tn}$ for the candidate closed loop solution.
\item Evaluate $\hat{X}^\# \models \Psi$. If the verification holds we have a solution, and exit the loop.
\end{enumerate} 
\item If the candidate solution is not valid we refine the abstraction used by the synthesizer
\begin{enumerate}
\item Find the constraints that invalidate the property. These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to obtain a set of counterexamples for the eigenvalues, which we define as $\phi(\Lambda)$. This is a constraint in the spectrum (\emph{ie} frequency response transfer function) of the closed loop dynamics. 
\item Transform the soft constraints on the spectrum into soft constraints on the coefficients of the characteristic polynomial. 
$z^n+\sum_{i=1}^n[a_i-k_i]z^{n-i}=\prod_{i=1}^n (z-[\lambda_i]) : |[\lambda_i]|<1 \wedge [\lambda_i] \models \phi_{\Lambda}$.
\item Pass the refined abstraction with the new constraints to the synthesizer, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. We note that the Abstraction refinement is a soft constraint on the proposed model which can increase or decrease the parameter space at any time, whereas the concrete counterexample passed to the synthesizer is monotonically decreasing. The first one improves speed of the tool whereas the second ensures convergence.

@@

Table~\ref{table:State-space benchmarks} summarises all benchmarks extracted 
from the control system literature~\cite{Franklin15,maglev,converters,CTMS}. 
\textit{DC Motor Position and Rate} plants describes the angular position and 
velocity of a DC Motor, respectively, that coupled with wheels and cables provides 
translational motion. 
\textit{Aircraft Pitch Dynamics} plant represents the air vehicle orientation and 
control based on the pitch dimension. 
\textit{Ball Magnetic Levitation} plant describes a physical model to keep a 
metal ball hanged in air via a magnetic field . 
\textit{Buck Converter} plant represents a power converter model that steps down 
voltage from the supply to the load while stepping up current. 
\textit{Boost Converter} plant also represents a power converter model, but here 
it steps up voltage from the supply to the load while stepping down current. 
\textit{Buck-boost Converter} plant represents a converter model that has an output 
voltage magnitude, which is either greater than or less than the input voltage magnitude.

\textit{Automotive Cruise System} plant describes a physical model that represents 
the speed of a motor vehicle. 
\textit{Helicopter Longitudinal Motion} plant provides the 
longitudinal motion model of a helicopter. 
\textit{Inverted Pendulum} plant describes a pendulum model
with its center of mass above its pivot point. 
\textit{Magnetic Suspension} plant provides the physical model for which 
a given object is suspended via a magnetic field. 
\textit{Magnetized Pointer} plant describes a physical model that is rotated through interaction 
with magnetic fields (typically employed in analogue gauges and indicators).
\textit{1/4 Car Suspension} plant presents a physical model that connects a car to its wheels 
and allows relative motion between both parts.
\textit{Computer Tape Driver} plant describes a physical model to read and write data 
on a storage device in the computer.
\textit{USCG Cutter Tampa Heading Angle} plant presents a physical model 
for the yaw angle dynamics of a US warship USCG Cutter Tampa.

@@

%-------------------------------
\subsection{Threats to validity}
%-------------------------------
We report an assessment of both our approaches over a diverse set of real-world benchmarks. Nevertheless, this set of benchmarks is limited within the scope of this paper and the performance may not generalise to other benchmarks.
